---
title: "Unit Conversion App"
author: "LG Chew"
date: "June 14, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This app is created to convert frequently used items
from imperial system to metric system.

Items included for this app:

- Weight
- Height
- Length
- Temperature
- Volume
- Speed

## The Idea Behind

The idea of creating this app is because most countries uses metric system,
while in the United States, imperial system is used.

This app will be useful for everyone, such as:

- foreign students who study in the US
- foreign workers who are employed to work in the US
- media when dealing with US related news

## Process

Users will need to input on the left side of the app,
and the result will be displayed on the right side.

Simple example of code for converting weight from lb to kg

```{r}
inweight = 100
wtInput <- as.numeric(inweight)
wtconv <- wtInput/2.205
wtconv
```

## Summary

You may access this app in the following link:
<https://leongghee.shinyapps.io/UnitConversion>

Source code can be viewed from here:
<https://github.com/leongghee/UnitConversionShinyApp>
